Self recovering capabilities in images using the BPCS Steganography algorithm

### 2014-10-06 Paper/main.tex
First refactoring of chapter 2

This section gives a brief description of the concepts used in this report.
The reasoning behind the proposed method will also be explained in \ref{introQualityIncrease} and \ref{introHighCap}.
This will serve to to show the applicability of the proposed method as well as the shortcomings it attempts to address.

\subsection{Overview}
Self recovering images (described in \ref{introSelfEmbedRecovery}) poses an interesting problem.
There is an inherent trade-off (described in \ref{introQualityTrade}) between the quality of the image after embedding and the quality of the image after recovery.
This report proposes a method in which a high capacity image steganography embedding algorithm (described in \ref{introHighCap}) is applied to the problem of self-recovering images to attempt to increase the quality of the images (described in \ref{introQualityIncrease}) both after embedding and after recovery.

@@

>>>>

\subsection{Introduction}
//TODO
Self-recovering images are images that have their own image content embedded into themselves using image steganography techniques. 
This content can then be extracted from the image at a later stage in order to reconstruct the image to an approximate original state in the case that the image was damaged.

\hspace{0pt} \\
In order to understand the self-recovering system proposed in this dissertation, one has to understand the underlying technologies.  This chapter will look at image steganography in more detail in section \ref{introSteganography} and at watermarking in section \ref{introFragWatermarking}  Self-embedding and recovery will be discussed in section \ref{introSelfEmbedRecovery} as well as the inherent quality trade off in section \ref{introQualityTrade} with a conclusion in section \ref{introConclusion}

Self recovering images poses an interesting problem.
\hspace{0pt} \\
//TODO insert formal definition here
\hspace{0pt} \\
There is an inherent trade-off between the quality of the image after embedding and the quality of the image after recovery.

\iffalse
//TODO possibly remove this
This report proposes a method in which a high capacity image steganography embedding algorithm (described in \ref{introHighCap}) is applied to the problem of self-recovering images to attempt to increase the quality of the images (described in \ref{introQualityIncrease}) both after embedding and after recovery.
\fi

@@

\subsection{Conclusion}
\label{introConclusion}
//TODO
